% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Projects besides Work Experience}{\faLaptop}

\begin{projects}
	\project
	{LibSOFL}{2023-Present}
	{LibSOFL is a transaction runtime analysis library for EVM-compatible blockchain. It provides convenient APIs to quickly replay historical transactions and analyze the execution trace. The library is the basis of my research work in blockchain security analysis.}
	{\textit{Reqeust for access}}
	{Rust, Ethereum, Web3, Blockchain, Security, Analysis}

	\project
	{Nyx}{2023}
	{Nyx is a Solidity static analyzer aiming to detect front-running vulnerabilities in smart contracts. It is the deliverable of my research work in blockchain security analysis.}
	{\textit{Reqeust for access}}
	{Rust, Ethereum, Web3, Blockchain, Security, Analysis}


	\project
	{Slither}{2023}
	{\github{https://github.com/crytic/slither}}
	{Slither is a static analysis framework for Solidity smart contracts. I am a contributor to Slither in terms of control flow graph (CFG) and SlithIR construction.}
	{Python, Solidity}

	\project
	{Redgiant}{2021 - 2022}
	{\github{https://github.com/Troublor/erebus-redgiant}}
	{Project Redgiant is a runtime analysis framework for EVM bytecode. It is capable of doing customized trace analysis or data flow analysis in the execution of Ethereum transactions. I build it as a research tool to develop techniques to automatically identify front-running attacks on the blockchain and build vulnerability benchmarks.}
	{Go, Ethereum}

	\project
	{ĐArcher}{2020 - 2021}
	{\github{https://github.com/Troublor/darcher}}
	{ĐArcher is a framework for testing Ethereum-based decentralized applications (DApps). As a research project, I identify a new type of bug in DApps, called on-chain-off-chain synchronization bugs, and propose ĐArcher to automatically detect them in DApps.}
	{TypeScript, Java, Go, Solidity, Ethereum}

	\project
	{ulauncher-numconverter}{2021}
	{\github{https://github.com/Troublor/ulauncher-numconverter}\website{https://ext.ulauncher.io/-/github-troublor-ulauncher-numconverter}{Number Converter - Ulauncher Extensions}}
	{ulauncher-numconverter is a Ulauncher extension that converts numbers between different bases.}
	{Python, Ulauncher}


	\project
	{My Personal Website}{2019 - Present}
	{\github{https://github.com/Troublor/troublor.github.io}\website{https://troublor.xyz}{troublor.xyz}}
	{I build my personal website by hand using React and TypeScript, instead of filling static templates like Hugo and Gatsby framework.}
	{React, Typescript, CSS, HTML}

\end{projects}
